An Elastica-driven Digital Curve Evolution Model for Image Segmentation\thanks{This work has been partially funded by CoMeDiC ANR-15-CE40-0006 research grant.}

### 2019-11-28 jmiv.tex
glued curve change in definition

\begin{definition}[Glued Curve]
Given closed curves $C_1,C_2$ agreeing with some orientation $q$, a glued curve is a closed curve  $(c_1,\ell_1,c_2,\ell_2)$ with orientation $q$ and $c_1 \in C_1, c_2 \in C_2$. The linels $\ell_1,\ell_2$ are called junction linels.
\end{definition}

>>>>

\begin{definition}[Glued Curve]
Given a closed curve $C_1$ with orientation $q$, and curve $C_2$ with same orientation $q$ such that $C_2$ encloses a region that contains $C_1$, a glued curve is a closed curve  $(c_1,\ell_1,c_2,\ell_2)$ with orientation $q$ and $c_1 \subset C_1, c_2 \subset C_2$. The linels $\ell_1,\ell_2$ are called junction linels.
\end{definition}
